Efficient inference using the approximate Riemannian geometry of stochastic population models

### 2012-09-24 paper/paper.tex
Added bibtex file
Added figures to paper.

%\documentclass{pnasone}
\documentclass{pnastwo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Changing position of text on physical page:
%% Since not all printers position
%% the printed page in the same place on the physical page,
%% you can change the position yourself here, if you need to:

@@

%\usepackage[dvips]{graphicx}

@@

% Sample bibliography item in PNAS format:
%% \bibitem{in-text reference} comma-separated author names up to 5,
%% for more than 5 authors use first author last name et al. (year published)
%% article title  {\it Journal Name} volume #: start page-end page.
%% ie,
% \bibitem{Neuhaus} Neuhaus J-M, Sitcher L, Meins F, Jr, Boller T (1991) 
% A short C-terminal sequence is necessary and sufficient for the
% targeting of chitinases to the plant vacuole. 
% {\it Proc Natl Acad Sci USA} 88:10362-10366.

%% Enter the largest bibliography number in the facing curly brackets
%% following \begin{thebibliography}

% \begin{thebibliography}{}
% 
% \end{thebibliography}

@@

>>>>

%\documentclass{pnasone}
\documentclass{pnastwo}
\bibliographystyle{pnas}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Changing position of text on physical page:
%% Since not all printers position
%% the printed page in the same place on the physical page,
%% you can change the position yourself here, if you need to:

@@

\usepackage{graphicx}

@@

% Sample bibliography item in PNAS format:

\bibliography{refs}    
%% Enter the largest bibliography number in the facing curly brackets
%% following \begin{thebibliography}

%  \begin{thebibliography}{}
% % \bibitem{in-text reference} comma-separated author names up to 5,
% % for more than 5 authors use first author last name et al. (year published)
% % article title  {\it Journal Name} volume #: start page-end page.
% % ie,
% \bibitem{Neuhaus} Neuhaus J-M, Sitcher L, Meins F, Jr, Boller T (1991) 
% A short C-terminal sequence is necessary and sufficient for the
% targeting of chitinases to the plant vacuole. 
% {\it Proc Natl Acad Sci USA} 88:10362-10366.
%  
%  \end{thebibliography}

@@

\begin{figure}[ht]
\begin{center}
\centerline{\includegraphics[]{../graphics/figure1}}
\end{center}
\caption{Stochastic simulation of the immigration-death process, with parameters
$k_1=k_2=1$ and $n(0)=0$. The black line shows the full stochastic realisation, 
the red dots indiciate the observed data.}
\end{figure}
\begin{figure*}[ht]
\begin{center}
\centerline{\includegraphics[width=.7\textwidth]{../graphics/figure2}}
\caption{Comparison of the exact and the moment closure expected fisher information matrix. \textit{Note: I'm not happy with the layout, still working on that}.}\label{afoto2}
\end{center}
\end{figure*}
% 
% \begin{figure*}
% \centering
% \includegraphics[]{../graphics/figure1}
% \caption{blah}
% \end{figure*}
